Characterizing hippocampal replay using hybrid point process state space models

### 2019-11-14 paper.tex

Point process state space models have been successful solution to categorizing different types of replay via their dynamics. Previously, we have used state space models with parallel point process filters to classify task dependent trajectories in a real-time setting \cite{DengRapidclassificationhippocampal2016}. In this previous work, there is only one dynamic state that can be selected. Here we extend that model to a general state-space state space framework for characterizing hippocampal replay. In particular, we show how this framework can: (1) allow for switching between discrete states by adding in a model of the discrete dynamics (2) used in offline analysis by adding a smoother, and (3) be flexible and interpretable by showing two examples of categorizing features of hippocampal replay.

>>>>

Point process state space models have been successful solution to categorizing different types of replay via their dynamics \cite{DengRapidclassificationhippocampal2016, TaoContributionsstatisticalanalysis2018, EdenCharacterizingComplexMultiScale2018}. Previously, we have used state space models with parallel point process filters to classify task dependent trajectories in a real-time setting \cite{DengRapidclassificationhippocampal2016}. In this previous work, there is only one dynamic state that can be selected. Here we extend that model to a general state-space state space framework for characterizing hippocampal replay. In particular, we show how this framework can: (1) allow for switching between discrete states by adding in a model of the discrete dynamics (2) used in offline analysis by adding a smoother, and (3) be flexible and interpretable by showing two examples of categorizing features of hippocampal replay.
